Bricking up backdoors in Intrusion Detection Systems

### 2019-09-12 paper/paper.tex
Fix typos

\subsection{Explainability Plots} \label{sec:plots}
%A major problem for the deployment of ML is the unpredictability and the lack of understanding of the decisions an ML models takes. For this reason, a
A number of methods has been proposed in the recent years aiming to visualize and explain a non-interpretable ML model's decisions.
Applied to the present problem, we can pick up ideas from \glspl{pdp} and \gls{ale} plots, not only for identifying backdoors in the \gls{mui}, but also for finding wrong decisions it would take due to flawed training data.

@@

As shown in \autoref{fig:pdp_ttl}, the \glspl{pdp} for \gls{dl} show a deep notch for certain low values of stdev(TTL). As discussed above, normal traffic is very unlikely to have deviating \gls{ttl} values for different packets. In contrast to \autoref{fig:pdp_ttl}, one would therefore expect this feature to have a negligible influence on the classification result. In our case, this notch thus points to the existance of the backdoor we embedded. For the \gls{rf} model the same pattern is observed but omitted for brevity.

>>>>

\subsection{Explainability Plots} \label{sec:plots}
%A major problem for the deployment of ML is the unpredictability and the lack of understanding of the decisions an ML models takes. For this reason, a
A number of methods have been proposed in the recent years aiming to visualize and explain a non-interpretable ML model's decisions.
Applied to the present problem, we can pick up ideas from \glspl{pdp} and \gls{ale} plots, not only for identifying backdoors in the \gls{mui}, but also for finding wrong decisions it would take due to flawed training data.

@@

As shown in \autoref{fig:pdp_ttl}, the \glspl{pdp} for \gls{dl} show a deep notch for certain low values of stdev(TTL). As discussed above, normal traffic is very unlikely to have deviating \gls{ttl} values for different packets. In contrast to \autoref{fig:pdp_ttl}, one would therefore expect this feature to have a negligible influence on the classification result. In our case, this notch thus points to the existence of the backdoor we embedded. For the \gls{rf} model the same pattern is observed but omitted for brevity.
